---
title: "Applying party pkg on ID3"
author: "Waniya"
date: "May 2, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PARTY Pkg in R studio Assignment

A computational toolbox for recursive partitioning.
The core of the package is ctree(), an implementation of
conditional inference trees which embed tree-structured
regression models into a well defined theory of conditional
inference procedures. This non-parametric class of regression
trees is applicable to all kinds of regression problems, including
nominal, ordinal, numeric, censored as well as multivariate response
variables and arbitrary measurement scales of the covariates.
Based on conditional inference trees, cforest() provides an
implementation of Breiman's random forests. The function mob()
implements an algorithm for recursive partitioning based on
parametric models (e.g. linear models, GLMs or survival
regression) employing parameter instability tests for split
selection. Extensible functionality for visualizing tree-structured
regression models is available. The methods are described in
Hothorn et al. (2006) <doi:10.1198/106186006X133933>,
Zeileis et al. (2008) <doi:10.1198/106186008X319331>  <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r }
library(party)
 Listofdrinks <- read.csv("D:/data mining/Listofdrinks.csv")
  View(Listofdrinks)
  set.seed(1234) 
ind <-sample(2, nrow(Listofdrinks), replace=TRUE, prob=c(0.7,0.30))
  train.data <-Listofdrinks[ind==1,]
 test.data <-Listofdrinks[ind==2,]
 myf <- fixed.acidity ~ chlorides+pH+alcohol
 Listofdrinks_ctree <-ctree(myf,data=train.data)
```

## Decission Tree of data

You can also embed plots, for example:

```{r }
plot(Listofdrinks_ctree)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
